EDLD 651 Final Project Presentation

### 2020-11-26 presentation.Rmd
changes to pres
continued working on my sections

## Next R hurdle to tackle
- remove outliers and re-run analysis
- power analysis
- adapt and develop the study
- run an online study
- replicate with cellular automata and 3D dynamic fractals

@@

- Invented by Benoit Mandelbrot in 1980
  *"Clouds are not spheres. Mountains are not triangles."*
- Measure of "roughness" called dimension
- Self similarity and scale invariance
- Mathematically or algorithmically generated
- Pervasive in nature

@@

## Ben

## Tess

## Scott

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="360" width="480">

>>>>

## Next R hurdle to tackle
- remove outliers and re-run analysis
- run a power analysis
- adapt and develop the study
- run an online study
- replicate with cellular automata and 3D dynamic fractals

@@

:::: {style="display: flex;"}

:::{}
- Invented by Benoit Mandelbrot in 1980
- *"Clouds are not spheres. Mountains are not triangles."*
- Measure of "roughness" called dimension
- Self similarity and scale invariance
- Mathematically or algorithmically generated
:::

:::{}
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/cloud5.png" height="300" width="400">
:::

::::

## Where are fractals?...Everywhere!
Fractals are pervasive in natural processes.

:::: {style="display: flex;"}

::: {}
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mountain2.png" height="200" width="300">
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/purple.png" height="200" width="300">
:::

::: {}
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/veins2.png" height="200" width="300">
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/tree2.png" height="200" width="300">
:::

::: {}
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/river3.png" height="200" width="300">
<img src="C:/Users/sgwallner/Downloads/r_projects/final_project/Natural Fractals/mud.png" height="200" width="300">
:::

::::

@@

## 
<!-- Ben -->

## 
<!-- Tess -->

## 
<!-- Scott -->

###
<small> Dwell times ***increase*** as complexity ***increases*** during the ***growth*** phase.
</small>

<small>Dwell times ***decrease*** as complexity ***decreases*** during the ***decay*** phase.
</small>

@@

<img src="/Users/sgwallner/Downloads/r_projects/final_project/presentation_images/00scott.png" height="480" width="640">
